Honey Bee Colonies Impacted by Varroa, American Fouldbrood and Global Warming

### 2024-08-01 starter-analysis-exercise/products/report/starter-analysis-report.qmd
HTML5

---
title: "Honey Bee Colonies Impacted by Varroa, American Fouldbrood and Global Warming"
author: Edward Cruz, Jr, Leonel G. Salazar, Amelia Tristan, Mojisola Popoola
format: html
editor: 
  markdown: 
    wrap: 72
---

>>>>

---
title: "Honey Bee Colonies Impacted by Varroa, American Fouldbrood and Global Warming"
subtitle: ""
author: Edward Cruz, Jr, Leonel G. Salazar, Amelia Tristan, Mojisola Popoola
date: today
format:
  html:
    toc: false
    number-sections: true
    highlight-style: github
bibliography: ../dataanalysis-template-references.bib
csl: ../apa.csl
editor: 
  markdown: 
    wrap: 72
---
